On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-04-17 ms-suppinfo.Rnw
Editorial change: end of results moved in discussion Table 2 moved to supplementary material

>>>>

\clearpage
 \begin{table}[h!]
 \centering
 \caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
 {\footnotesize
 \vspace{0.5cm}
 \begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
   \hline
   & Quality criteria & Check & How and where is it addressed?\\
   \hline
   1.& Reporting full details of bibliographic searches & yes  & Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
   2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
   3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See ``Material and Methods'' for details.\\
  4.& Specifying meta-analytical model & yes & We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
  5.& Quantifying heterogeneity in effect sizes &  yes & We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
  6.& Exploring causes of heterogeneity & yes &  We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
  7.& Multifactorial analysis of explanatory variable  & yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
   8.& Testing for publication bias &  yes & We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
   9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
   10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\
   11.& Controlling for phylogeny &  no &  It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
   12.& Specifying the software used & yes & See sections in ``Material and Methods'' and ``Availability of code and data''.\\
  13.& Providing reference list of primary studies included in the analysis &  yes & All articles from which data were extracted are cited in the paper.\\
   14.& Providing the data set used for meta-analysis  & yes & A copy of the data set is available. See ``Availability of code and data'' for details.\\
    \hline
 \end{tabular}
 }
 \label{tab:meta}
 \end{table}
